A Quantitative Approach to Book Printing in Sweden and Finland, 1640–1828: supplementary material

### 2018-12-11 inst/examples/201808-HistoricalMethods-Supplement.Rmd
Swedish gap analysis

```{r languages_fen, echo=FALSE, message=FALSE, warning=FALSE}
tab <- top(fen, field, 10, "data.frame", round = 1)
colnames(tab) <- gsub("language_primary", map("language_primary", fieldname_table(), from = "Data", to = "Name"), colnames(tab))
knitr::kable(tab, format = "markdown")
```

>>>>

```{r languages_fen, echo=FALSE, message=FALSE, warning=FALSE}
map <- bibliographica::map
tab <- top(fen, field, 10, "data.frame", round = 1)
colnames(tab) <- gsub("language_primary", map("language_primary", fieldname_table(), from = "Data", to = "Name"), colnames(tab))
knitr::kable(tab, format = "markdown")
```
